Nonlinear Spatio-Temporal Modelling using the Integro-Difference Equation

### 2010-07-08 ltx/second_order_framework/second_order_manuscript.tex
added the aims to the 2nd order paper

%to delete
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
%opening
\title{Nonlinear Spatio-Temporal Modelling using the Integro-Difference Equation}
\author{Parham Aram*,
        Dean~R.~Freestone,Kenneth Scerri, Michael Dewar,\\ Andrew Zammit Mangion and Visakan Kadirkamanathan}

@@

\begin{abstract}

@@

@@

where $v_t(\mathbf r)$ denotes a spatio-temporal field at time $t$ and at spatial location $\mathbf r$, $f(.)$ is a nonlinear map, and $w(.)$ is a spatial mixing kernel. The disturbance, $\mathbf e_{t-p}(\mathbf r)$, is a zero-mean normally distributed noise process that is spatially

@@

and $\delta(.)$ is the Dirac-delta function.

@@

where $c$ is the center of the kernel. To make the simplification, we first define

@@

\section{Deterministic second order neural field model}

@@

The above second order differential equation can be split into two, coupled first order ODEs.\\

@@

Now we approximate the two first-order ode by Euler's method

>>>>

%to delete
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{yellow}{#1}}}}}

%opening
\title{Nonlinear Spatio-Temporal Modelling using the Integro-Difference Equation}
\author{Parham Aram*,
        Dean~R.~Freestone,Kenneth Scerri, Michael Dewar,\\ Andrew Zammit Mangion and Visakan Kadirkamanathan}

@@

\begin{abstract}
The aim of this paper is to 	
\begin{enumerate}
	\item Derive the temporally second order model
	\item Apply the EM algorithm on test data generated by the model above
	\item Extend the EM algorithm to estimate also the model covariances
	\item Apply method above to measured data
\end{enumerate}

@@

\begin{enumerate}
	\item General background and motivation
	\item Aims and hypotheses
	\item Specific background
	\item Point out specific things we are doing and why they are important
	\item Paper layout
\end{enumerate}

@@

where $v_t(\mathbf r)$ denotes a spatio-temporal field at time $t$ and at spatial location $\mathbf r$, $f(\cdot)$ is a nonlinear map, and $w(\cdot)$ is a spatial mixing kernel. The disturbance, $\mathbf e_{t-p}(\mathbf r)$, is a zero-mean normally distributed noise process that is spatially

@@

and $\delta(\cdot)$ is the Dirac-delta function.

@@

where $c$ is the center of the kernel. \dean{Can't use c as it is used in the observation matrix.} To make the simplification, we first define

@@

\section{Deterministic Second-Order Neural Field Model}

@@

The above second-order differential equation can be split into two, coupled first order ODEs.\\

@@

Now we approximate the two first-order ODE by Euler's method
